FictionEro - Affective Impact of Fiction

### 2025-11-10 analysis/analysis.qmd
Update analysis.qmd

```{r Arousal2}
#| fig-width: 12
arousal_dist2 <- df2 |>
  ggplot(aes(x=Arousal, fill = Condition)) +
  geom_bar(position = "identity", alpha = 0.5, line = "black") +
  scale_y_sqrt(expand = c(0, 0)) +
  scale_x_continuous(breaks = c(0, 1)) +
  labs(title = "Arousal Study 2", ) +
  facet_wrap(~Gender) +
  scale_fill_manual(values=c("Photograph"="#F44336", "AI-Generated"="#2196F3")) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))

```{r Arousal2}
#| fig-width: 12
arousal_dist2 <- df2 |>
  ggplot(aes(x=Arousal, fill = Condition)) +
  geom_bar(position = "identity", alpha = 0.5, line = "black") +
  scale_y_sqrt(expand = c(0, 0)) +
  scale_x_continuous(breaks = c(0, 1)) +
  labs(title = "Arousal Study 2", ) +
  facet_wrap(~Gender) +
  scale_fill_manual(values=c("Photograph"="#F44336", "AI-Generated"="#2196F3")) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))

@@

```{r Arousal2}
#| fig-width: 12
enticement_dist2 <- df2 |>
  ggplot(aes(x=Enticing, fill = Condition)) +
  geom_bar(position = "identity", alpha = 0.5, line = "black") +
  scale_y_sqrt(expand = c(0, 0)) +
  scale_x_continuous(breaks = c(0, 1)) +
  labs(title = "Enticment Study 2", ) +
  facet_wrap(~Gender) +
  scale_fill_manual(values=c("Photograph"="#F44336", "AI-Generated"="#2196F3")) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))

@@

```{r Arousal2}
#| fig-width: 12
valence_dist2 <- df2 |>
  ggplot(aes(x=Valence, fill = Condition)) +
  geom_bar(position = "identity", alpha = 0.5, line = "black") +
  scale_y_sqrt(expand = c(0, 0)) +
  scale_x_continuous(breaks = c(0, 1)) +
  labs(title = "Valence Study 2", ) +
  facet_wrap(~Gender) +
  scale_fill_manual(values=c("Photograph"="#F44336", "AI-Generated"="#2196F3")) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))

valence_dist2
```

### Average Arousal

@@

@@

```{r}
arousal1 <- readRDS("models/ModelArousal_1.rds")
arousal2 <- readRDS("models/ModelArousal_2.rds")
```

@@

```{r}
params_table(arousal2)
summary(arousal2, robust = TRUE)

```{r}
#| fig-height: 8
#| fig-width: 8

make_combined_plot <- function(model1, model2 = NULL, 
                               title = "Estimated Marginal Means") {

  df1 <- modelbased::estimate_means(
    model1, by = c("Gender", "Relevance", "Condition", "ConditionBelief"),backend = "emmeans") |>
    dplyr::mutate(Sample = "Study 1") |>
    as.data.frame()

  # Study 2: only Relevant
  if (!is.null(model2)) {
    df2 <- modelbased::estimate_means(
      model2, by = c("Gender", "Condition", "ConditionBelief"), backend = "emmeans") |>
      dplyr::mutate(Relevance = "Relevant", Sample = "Study 2") |>
      as.data.frame()
    pred_df <- rbind(df1, df2)
  } else {
    pred_df <- df1
  }

  plt <- pred_df |>
    ggplot(aes(x = ConditionBelief, y = Estimate,color = Condition, linetype = Sample, group = interaction(Sample, Condition)
    )) +
    geom_hline(yintercept = 0, color = "darkgrey") +
    geom_line(linewidth = 1) +
    geom_point(size = 2) +
    geom_errorbar(aes(ymin = CI_low, ymax = CI_high), width = 0.1) +
    facet_grid(Relevance ~ Gender, switch = "y") +
    scale_color_manual(values = c("AI-Generated" = "#2196F3","Photograph" = "#F44336")) +
    theme_minimal(base_size = 14) +
    labs(title = title, x= "Whether the original labels were believed to be true",color = "Images presented as:", linetype = "Sample"
    ) +
    theme(
      axis.title.y = element_blank(),
      axis.text.y = element_text(size = 8),
      strip.placement = "outside",
      strip.background.x = element_rect(fill = "lightgrey", color = NA),
      strip.text.x = element_text(size = 10),
      strip.text.y = element_text(size = 10),
      axis.text.x = element_text(face = "bold", size = 9, color = "black"),
      legend.text = element_text(size = 10),
      legend.position = "bottom")

  plt
}

plta <- make_combined_plot(arousal1, arousal2, title = "Arousal Estimates for All Stimuli")

plta
```

### Enticement

```{r}
enticement1 <- readRDS("models/ModelEnticement_1.rds")
enticement2 <- readRDS("models/ModelEnticement_2.rds")
```

```{r}
params_table(enticement1)
summary(enticement1, robust = TRUE)
```

```{r}
params_table(enticement2)
summary(enticement2, robust = TRUE)

```{r}
#| fig-height: 8
#| fig-width: 8

plt_e <- make_combined_plot(enticement1, enticement2, title = "Enticement Estimates for All Stimuli")
plt_e
```

### Valence

```{r}
valence1 <- readRDS("models/ModelValence_1.rds")
valence2 <- readRDS("models/ModelValence_2.rds")
```

```{r}
params_table(valence1)
summary(valence1, robust = TRUE)
```

```{r}
params_table(valence2)
summary(valence2, robust = TRUE)

```{r}
#| fig-height: 8
#| fig-width: 8

plt_v <- make_combined_plot(valence1, valence2, title = "Valence Estimates for All Stimuli")
plt_v
```

>>>>

```{r Arousal2}
#| fig-width: 12
arousal_dist2 <- df2 |>
  ggplot(aes(x=Arousal, fill = Condition)) +
  geom_bar(position = "identity", alpha = 0.5, colour = "black") +
  scale_y_sqrt(expand = c(0, 0)) +
  scale_x_continuous(breaks = c(0, 1)) +
  labs(title = "Arousal Study 2", ) +
  facet_wrap(~Gender) +
  scale_fill_manual(values=c("Photograph"="#F44336", "AI-Generated"="#2196F3")) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))

@@

```{r Arousal2}
#| fig-width: 12
enticement_dist2 <- df2 |>
  ggplot(aes(x=Enticing, fill = Condition)) +
  geom_bar(position = "identity", alpha = 0.5, colour = "black") +
  scale_y_sqrt(expand = c(0, 0)) +
  scale_x_continuous(breaks = c(0, 1)) +
  labs(title = "Enticment Study 2", ) +
  facet_wrap(~Gender) +
  scale_fill_manual(values=c("Photograph"="#F44336", "AI-Generated"="#2196F3")) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))

@@

```{r Arousal2}
#| fig-width: 12
valence_dist2 <- df2 |>
  ggplot(aes(x=Valence, fill = Condition)) +
  geom_bar(position = "identity", alpha = 0.5, colour = "black") +
  scale_y_sqrt(expand = c(0, 0)) +
  scale_x_continuous(breaks = c(0, 1)) +
  labs(title = "Valence Study 2", ) +
  facet_wrap(~Gender) +
  scale_fill_manual(values=c("Photograph"="#F44336", "AI-Generated"="#2196F3")) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))

valence_dist2
```
:::

## Average Arousal

### Study 1

@@

### Study 2

@@

<!-- Study 2 Arousal:  Draws: 96 chains, each with iter = 2000; warmup = 1000; thin = 1; total post-warmup draws = 96000 -->

<!-- Study 2 Arousal: Draws: 80 chains, each with iter=2000; warmup=1000; thin=1; post-warmup draws per chain=1000, total post-warmup draws=80000. -->
```{r}
arousal1 <- readRDS("models/ModelArousal_1.rds")
arousal2 <- readRDS("models/ModelArousal_2.rds")
```

#### Posterior Description

<!-- Sampling Diagnostics -->

<!-- - ESS should be at least 1000 (the effective sample size - ESS - is an estimation of the number of independent samples) -->

<!-- - R^(“R-hat”) Should be lower than 1.01 (R-hat is a measure of convergence) -->

@@

```{r}
params_table(arousal2) 
summary(arousal2, robust = TRUE)
```

#### Model Performance

```{r}
performance::performance(arousal1)
```

```{r}
performance::performance(arousal2)
```
